\documentclass[11pt,a4paper,sans]{moderncv}
\usepackage[utf8]{inputenc}
\usepackage[english]{babel}
\usepackage{multicol}
\moderncvstyle{classic}
\moderncvcolor{orange}
\nopagenumbers{}
%\usepackage[scale=0.80]{geometry}
\usepackage[margin=0.8in]{geometry}
\usepackage{moderntimeline}
\tlmaxdates{2011}{2016}

\firstname{Guillaume}
\familyname{Dupuis}
\title{CS student at EPITA}
\email{g.dupuis.tourniaire@gmail.com}
%\homepage{phenixnest.com}
\mobile{+33 638~536~409}

\quote{Passionnate computer scientist, mostly interested in system
developpement, embedded system, infrastructure and Internet of things}
\begin{document}
\makecvtitle

\section{Experience}
\tlcventry{2014}{2016}{Teacher assistant in computer science}{EPITA}{}{}{
\textbf{Teaching} Shell, C, C++, Java, SQL and design pattern to 300 students.}
\tldatecventry{2014}{R\&D student}{Thales Communication \& Security}{Paris}
{}{Developed secure embedded systems in light virtualization for mobile device\\
\textbf{Technologies used:} LXC, Android, Debian, debootstrap.}
\tldatecventry{2013}{Electrician \& service support}{AFP}{Paris}{}{Gave
electrical service support for desks and datacenter of AFP (French Press
Agency).}
\subsection{Scholar projects}
\tldatecventry{2014}{Malloc}{C}{}{Implementation of malloc of libc.}{}
\tldatecventry{2014}{42sh}{C}{}{A posix shell in C done in course in teams of
5. I mostly did the command line and prompt, execution, built-in and
\texttt{fnmatch()} all written from scratch.}{}
\tldatecventry{2014}{Tiger}{C++}{}{Developped a compiler of tiger language in
teams of 3.}{
\textbf{Technologies used:} Flex, Bison, C++ 11.}
\tldatecventry{2013}{Electrician \& service support}{AFP}{Paris}{}{Gave
\tldatecventry{2015}{STOS}{C/ASM}{}{x86 kernel intended to teach interruptions
and memory management.}{}
\tldatecventry{2015}{Domobox}{Python}{}{Modular IOT box for monitoring some
devices at home.}{
\textbf{Technologies used:} Python3, Raspberry pi 2, arduino, MongoDB.}
\subsection{Spare time projects}
\tlcventry{2015}{0}{Linux Server Administration}{}{}{}{Administration and
configuration of linux server.}
\subsection{Associations}
\tlcventry{2014}{0}{Student office}{}{}{}{Member of student Office of EPITA}
\tlcventry{2014}{2015}{Communication office}{}{}{}{Member of communication
staff student's team of EPITA.}

\section{Formation}
\tlcventry{2011}{2016}{CS Engineer}{EPITA}{French engineering school}{}{}
\tldatecventry{2013}{Exchange}{Stafford University}{Stafford}{Computer science
master}{Studied Computer Science during 6 months.}

\section{Computer skills}
\cvitem{OS}{Linux, Unix, Windows}
\cvitem{Languages}{C, C++, C\#, Java, {Python}, shell, ASM x86, ADA}
\cvitem{Tools}{\textbf{Git}, vim, Visual Studio, project managment(MS Project), MicroEj}

\end{document}
